---
title: "CONCOR Example"
author: "Tyme Suda"
date: "11/26/2019"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Setup

Load in the required functions and data, igraph is required but is loaded when sourcing CONCOR.R. For this example we will use the Krackhardt high-tech managers data.

```{r CONCORsetup, include=TRUE, message=FALSE}
load("HighTech.Rdata")
library(igraph)
source('CONCOR.R')
source('CONCOR_supplemental_fun.R')
source('CONCOR_blockmodeling.R')
```


## Running CONCOR

Create the adjacency matrixes from each igraph object of interest.

```{r adjacency}
m0=get.adjacency(gadvice, sparse = FALSE)
m1=get.adjacency(gfriend, sparse = FALSE)
m2=get.adjacency(greport, sparse = FALSE)
```

Store the adacency matrixes denoting all relationships of interest within a single list. Fora single relationship simply put it in a list of length 1. If multple relationships are used the matrixies MUST be of the same size.

```{r listing}
m.list1=list(m0)
m.list2=list(m0,m1)
m.list3=list(m0,m1,m2)
```

To check that both node names and adjacency matrix sizes, agree in adition to checking that node names exist (and adding them if they don't) the `concor.vlaiditycheck` function can be used. Below it can be seen that with valid input no warnigs are thrown, and this works even for a singular relation (where it simply checks that node names exist).
```{r validity_check}
m.list1=concor.vlaiditycheck(m.list1)
m.list2=concor.vlaiditycheck(m.list2)
m.list3=concor.vlaiditycheck(m.list3)
```
Now if there is something wrong with the inputs it starts to vigurously wave red flags at you, as shown below.

```{r}
m1=matrix(c(1,2,3,4),2)
colnames(m1)=c("n","m")
rownames(m1)=c("n","m")
m2=matrix(c(5,6,7,8),2)

#concor.vlaiditycheck(list(m1, m2)) fails and gives error: "Node name mismatch" due to m2 not having names but m1 having them
concor.vlaiditycheck(list(m2, m2)) #adds node names but warns you that it did
#concor.vlaiditycheck(list(m1, m0)) gives error: "Adgacency matrixes of mixmatched sizes" due to matrixies of differing sizes being inputed

```


Once the adgacency matrixies are stored within a list and they are confirmed to be valid inputs, CONCOR can be run. It will split the matrix and continue to split each subsequent, smaller matrix until the specified number of splits are made. If the specified number of splits would cause structurally equivalent nodes to be split, or a single node to be split, the CONCOR algorithm will fail. In addition, the current version seperates all isolated nodes into their own block before running concor.

The output from concor is matrix with the first coumn being the block membership and the second being the node's name. The row names are simply the arbitrary order they are returned in.


### Example

Shown below are all possible splits of the gadvice data from the Krackhardt high-tech managers data and the first failing split. The output from the 2nd and 4th (last possible) splits are displayed.

```{r CONCORrun}
C1.1=concor(m.list1, p=1)
C1.2=concor(m.list1, p=2)
C1.3=concor(m.list1, p=3)
C1.4=concor(m.list1, p=4)
#C1.5=concor(m.list1, p=5)
```

The second split

```{r s1.2}
C1.2
```

The fourth split

```{r s1.4}
C1.4
```

It can be seen that in the fourth split multiple nodes have become isolated in their own blockings, so further splits will in turn fail.

## For Multiple Relationships

When multiple realationships are to be considerd the adjacency matrixies must be put into a single list. This was done above when I showed some of the possible lists. For this I will use `m.list2=list(m0,m1)` comprised of the advice and friendship relationships.

Once listed together running CONCOR for multiple relations is identical to a single relation.

```{r CONCORmulti}
C2.1=concor(m.list2, p=1)
C2.2=concor(m.list2, p=2)
C2.3=concor(m.list2, p=3)
C2.4=concor(m.list2, p=4)
#C2.5=concor(m.list2, p=5)
```

The output for the second split is shown below.

```{r s2.2}
C2.2
```

## Using the CONCOR Outputs

Once CONCOR has been run and block membership is determined, there are a near unending number of things one can do to understand and represent the data. Two of the simplest ways are plotting the network with color representing block membership and blockmodeling. Functions to do both are included in the file `CONCOR_supplemental_fun.R`.

To start either the CONCOR splits must be added as vertex attributes. This can be done using the function `blk.apply` if the CONCOR outputs have been previously saved or by simply using the `make.igraph` function that will run CONCOR and apply the outputs as the vertex attribute `csplitn` whre n is the split specified. Both functions are located in the `CONCOR_supplemental_fun.R` file. 

The inputs of `blk.apply` are the igraph object you created the splits from, the split, and a name to give the new vertex attribute. This is shown below for all four splits for the advice nework from the Krackhardt high-tech managers data.

```{r addCONattrib}
gadvice=blk.apply(gadvice, C1.1, "split1")
gadvice=blk.apply(gadvice, C1.2, "split2")
gadvice=blk.apply(gadvice, C1.3, "split3")
gadvice=blk.apply(gadvice, C1.4, "split4")

gadvice
```

The same can simply be be done without first running CONCOR by using `make.igraph` function on the list of adgacency matrixies you are intrested in and the split number you want, as shown below for the second split. This has the advantage of returning the split added to igraph objects for each relationship.

```{r addCONattrib2}
make.igraph(m.list2, 2)

```
While a thrid opption and probably the most usfull for this situation, of having igraph objects to start, is to run `concor.igraph.apply` on the list of igraph objects of intrest. This does the same thing as `make.igraph` but the input list is of igraph objects not the adgacency matrixies.

```{r addCONattrib3}
inp=list(gadvice, gfriend)
#add first and second splits
adv.freind.igraph=concor.igraph.apply(inp, 1)
adv.freind.igraph=concor.igraph.apply(adv.freind.igraph, 2)
adv.freind.igraph

```
The main reson to use this method is that any existing vertex atributes are kept unlike when using `make.igraph`.

### PLotting the network

To plot the network with block memebership represented by a colour, the function `concor.plot` can be used from `CONCOR_supplemental_fun.R` simmply because it is easier than saying `plot(iobject, vertex.color=vertex.attributes(iobject)[[split.name]], vertex.label=NA, vertex.size= 5,edge.arrow.size=.3)` every time you want to plot one of your networks. Although in all likelihood this function will need to be tweaked for individual use simply becuse you want your nodes to be a diffrent size or to use another colour scheme. The inputs for this function are the igraph object, the name of the split you want to represent, and a title.

The function is used below to plot the first and second splits of the advice network based off the splits found when using `gadvice` and `gfriend`.

``` {r plotNET}
concor.plot(adv.freind.igraph[[1]], 1)
title(main="I am the first split")
concor.plot(adv.freind.igraph[[1]], 2)
title(main="And I am the second split")


```

### Blockmodeling

Blockmodeling is something that is built into the library `statnet`, or more specifically its dependent package `SNA`. For the purposes of creating blockmodels based off the CONCOR outputs, a function that uses `SNA` was created called `make.blk` in `CONCOR_blockmodeling`. This function creates a list of blockmodel type objects one for each relation inputed in the list `adj.list`, the first input for the specified CONCOR splitting (the second input). It must be noted that `adj.list` must be a list of adjacency matrixies even if only one relation is being looked at and the output is a list of the blokmedel type objects ready to be plotted with either `plot.blk` or `plot.blk.labeless` if the labels don't look good for your data.

This is ran below for the second split for the advice and freindship networks treated as two relations.

```{r make.blk.shit}
m0=get.adjacency(gadvice, sparse = FALSE)
m1=get.adjacency(gfriend, sparse = FALSE)
bl2=make.blk(list(m0,m1), 2)
bl2
```

#### Ploting the blockmodel

Each element of the outputed list can be ploted with either `plot.blk` or `plot.blk.labeless` the plots for the advice blockmodel are shown below. The first is with labels the second without.


```{r }

plot.blk(bl2[[1]])
plot.blk.labeless(bl2[[1]])

```

Due to the high density of the connections in this network it is very hard to tell what is going on just from the blockmodel. To actually see how these blocks relate to each other it is much easier to look at the reduced graph.

#### Making the Reduced Graphs

To plot the reduced graphs a couple of function calls must be made, adjacency matrixies for each reruced graph must be created. This is done by using the `make.red` function. It takes the list of adqacency matrixies of intrest (one for each relation), the split number you want, and whether you want the output weighted or not (TRUE/FALSE) as inputs. This function then outputs a nested list, the first element `$red.mat` is the list of reduced matrixies, and the second part of the list, `$dens`, is the list of cutoff densities used (densities of the overall networks). This is shown below for the second split of the advice and freindship networks treated as two relations when weighted and unweighted.

```{r }

red.w=make.red(list(m0, m1), 2, weighted = TRUE)
red.w
red.uw=make.red(list(m0, m1), 2, weighted = FALSE)
red.uw

```

Once the reduced matrixies are made they can be plotted in igraph as networks by using the `make.red.igraph` function to make them into igraph objects then using `plot.red.weighted` or `plot.red.unweighted` depending on if they are weighted or not. Below The graphs of the weighted and unweighted reduced network plots for both the advice and freindship networks are shown.

```{r}

w.adv=make.red.igraph(red.w$red.mat[[1]])
plot.red.weighted(w.adv)
title(main="Advice Weighted")

uw.adv=make.red.igraph(red.uw$red.mat[[1]])
plot.red.unweighted(uw.adv)
title(main="Advice Unweighted")



w.frn=make.red.igraph(red.w$red.mat[[2]])
plot.red.weighted(w.frn)
title(main="Freindship Weighted")

uw.frn=make.red.igraph(red.uw$red.mat[[2]])
plot.red.unweighted(uw.frn)
title(main="Freindship Unweighted")


```


